### 2021-04-02 Chapter-4/Chapter-4.tex
Updates from Overleaf

        Observation ($o$)   & $A$ & $\neg A$ & $B$ & $\neg B$ \\ \hline
        Number of Solutions & 65526       & 10        & 32768     & 32768           \\ \hline
        Leaked Information (bits) & 0.0         & 14.7      & 1.0       & 1.0         \\
        \hline
    \end{tabular}
\end{table}
\section{Approximate Model Counting}
\label{MCreasons}
%According to
%Definition~\ref{def} introduced in \S\ref{sec:trace-qif},
%the problem of quantifying the amount of leaked information can be reduced to
%the problem of computing the number of items in $K^o$. However, we find that while
%there are various propositional model counters (e.g., \#SAT), they are not
%sufficient scalable for production cryptosystem analysis.
%there is no open source modulo theories counter (\#SMT) available.

%One straightforward method approximating the number of solutions is based on Monte Carlo
%sampling. However, the number of satisfying values could be exponentially small.
%Consider the formula $f_i\equiv{k_1} = 1\land{k_2} = 2\land{k_3} = 3\land{k_4} =
%4$, where $k_1$, $k_2$, $k_3$, and $k_4$ each represents one byte in the
%original sensitive input buffer, there is only one satisfying solution of total
%$2^{32}$ possible values, which requires exponentially many samples to get a
%tight bound. Monte Carlo method also suffers from the curse of dimensionality.
%For example, the length of an RSA private key can be as long as 4096 bits. If we
%take each byte (8 bits) in the original buffer as one symbol, the formula can
%have as many as 512 symbols.

%\vspace*{2pt}
%\textbf{Our Solution to Challenge C3:}
%We adopt multiple-step Monte Carlo sampling methods to count the number of
%possible inputs that satisfy the logic formula groups. The key idea is to split
%those constraints into several small formulas and sample them independently.
%We will introduce the method in the following subsection.

%\subsection{Information Leakage Estimation}

@@

According to the Definition~\ref{def}, to calculate the amount of leaked
information, the key is to calculate the cardinality
of $K^o$. Suppose an attacker can observe $n$ leakage sites, and each leakage
site has the following constraints: $c_{\addr{1}}, c_{\addr{2}}, \ldots,
c_{\addr{n}}$ respectively. The total leakage can be calculated from the constraint
$c_t({\addr{1}},{\addr{2}},\ldots,{\addr{n}}) = c_{\addr{1}} \land c_{\addr{2}}
\land \ldots \land c_{\addr{n}}$. 
%%The problem of estimating the total leaked
%%information can be reduced to the problem of counting the number of different
%%solutions that satisfies the constraint
%%$c_t({\addr{1}},{\addr{2}},\ldots,{\addr{n}})$. 
A simple method is to pick elements $k$ from $K$ and check if an
element is also contained in $K^o$. Assume $q$ elements satisfy this condition. In
expectation, we can use $\frac{k}{q}$ to approximate the value of
$\frac{|K|}{|K^o|}$.

@@

            \item Each time when we sample $c_t({\addr{1}},{\addr{2}},\ldots,{\addr{n}})$
            with a point, the sampling result is \emph{Satisfied} or not \emph{Not Satisfied}.
            The outcome does not depend on the result of 
            previous experiments. Also, as the amount of leaked information is calculated
            by a $\log$ function, we need not exactly count the number of solutions for 
            a given constraint.
            %\item For each constraint $F(C_{{addr}_i})$, the satisfying assignments
            %are close to each other, which means if we find one satisfying assignment, we 
            %are more likely to find other satisfying assignments nearby than randomly
            %pick one point in the whole searching space.

@@

>>>>

        Observation ($o$)   & $A$ & $\neg A$ & $B$ & $\neg B$ \\ \hline
        Number of Solutions & 65526       & 10        & 32768     & 32768           \\ \hline
        Leaked Information (bits) & 0.0         & 14.7      & 1.0       & 1.0         \\
        \hline
    \end{tabular}
\end{table}
\section{Approximate Model Counting}
\label{MCreasons}
According to
Definition~\ref{def} introduced in \S\ref{sec:trace-qif},
the problem of quantifying the amount of leaked information can be reduced to
the problem of computing the number of items in $K^o$. However, we find that while
there are various propositional model counters (e.g., \#SAT), they are not
sufficient scalable for production cryptosystem analysis.
there is no open source modulo theories counter (\#SMT) available.

One straightforward method approximating the number of solutions is based on Monte Carlo
sampling. However, the number of satisfying values could be exponentially small.
Consider the formula $f_i\equiv{k_1} = 1\land{k_2} = 2\land{k_3} = 3\land{k_4} =
4$, where $k_1$, $k_2$, $k_3$, and $k_4$ each represents one byte in the
original sensitive input buffer, there is only one satisfying solution of total
$2^{32}$ possible values, which requires exponentially many samples to get a
tight bound. Monte Carlo method also suffers from the curse of dimensionality.
For example, the length of an RSA private key can be as long as 4096 bits. If we
take each byte (8 bits) in the original buffer as one symbol, the formula can
have as many as 512 symbols.

%\vspace*{2pt}
%\textbf{Our Solution to Challenge C3:}
We adopt multiple-step Monte Carlo sampling methods to count the number of
possible inputs that satisfy the logic formula groups. The key idea is to split
those constraints into several small formulas and sample them independently.
We will introduce the method in the following subsection.

\subsection{Information Leakage Estimation}

@@

According to the Definition~\ref{def}, to calculate the amount of leaked
information, the key is to calculate the cardinality
of $K^o$. Suppose an attacker can observe $n$ leakage sites, and each leakage
site has the following constraints: $c_{\addr{1}}, c_{\addr{2}}, \ldots,
c_{\addr{n}}$ respectively. The total leakage can be calculated from the constraint
$c_t({\addr{1}},{\addr{2}},\ldots,{\addr{n}}) = c_{\addr{1}} \land c_{\addr{2}}
\land \ldots \land c_{\addr{n}}$. 
The problem of estimating the total leaked
information can be reduced to the problem of counting the number of different
solutions that satisfies the constraint
$c_t({\addr{1}},{\addr{2}},\ldots,{\addr{n}})$. 
A simple method is to pick elements $k$ from $K$ and check if an
element is also contained in $K^o$. Assume $q$ elements satisfy this condition. In
expectation, we can use $\frac{k}{q}$ to approximate the value of
$\frac{|K|}{|K^o|}$.

@@

            \item Each time when we sample $c_t({\addr{1}},{\addr{2}},\ldots,{\addr{n}})$
            with a point, the sampling result is \emph{Satisfied} or not \emph{Not Satisfied}.
            The outcome does not depend on the result of 
            previous experiments. Also, as the amount of leaked information is calculated
            by a $\log$ function, we need not exactly count the number of solutions for 
            a given constraint.

@@

\section{Implementation}

\tool{} consists of 16,729 lines of code in C++17 and Python. It has three
components: an Intel Pin tool that collects the execution trace, the
instruction-level symbolic execution engine, and the back-end that estimates
the information leakage.

\begin{table}[h!]
    \centering
    %    \resizebox{.8\columnwidth}{!}{
    \caption{\tool{}' main components and sizes}\label{tbl:implementation}
    \begin{tabular}{lr@{~}@{}l}
        \hline
        Component            & \multicolumn{2}{c}{Lines of Code (LOC)}             \\ \hline
        Trace Logging        & 501 lines                               & of C++    \\
        Symbolic Execution   & 14,963 lines                            & of C++    \\
        Data Flow            & 451 lines                               & of C++    \\
        Monte Carlo Sampling & 603 lines                               & of C++    \\
        Others               & 211 lines                               & of Python \\ \hline
        Total                & 16,729 lines                            &           \\\hline
    \end{tabular}
    %    }
\end{table}

Our current implementation supports most Intel 32-bit instructions that are essential to find address-based side-channel
vulnerabilities, including bitwise operations, control transfer, data movement, and logic
instructions. The tool uses the real values to update the registers and memory for instructions that the implementation does not support. 
Therefore, the tool may miss some leakages but will not raise false positives.

\section{Evaluation}

\section{Discussion}
While recent work found many side-channel vulnerabilities, 
we note that many of them have not been patched by developers.
Side-channels are ubiquitous in software and it would be difficult to fix all of them. 
We need a tool that estimates the sensitivity of each vulnerability
so software engineers can focus on
``severe'' leakages. For example, \tool{} reports that 
the modular exponentiation using square and multiply algorithms can
leak more information than a key validation function.

Software developers can use \tool{} to find severe vulnerabilities
and reason about countermeasures.
\tool{} estimates the amount of leaked information for each side-channel leakage
in one execution trace. \tool{} is useful for software
engineers to test programs and fix vulnerabilities.
The design, which is more precise in reporting true leakages as compared with other static
methods~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, obviously misses
leakages on unexplored traces. The amount of leaked information also depends on the secret key.
However, as the tool is intended for debugging and testing,
we think it is a software engineer's responsibility to select the input key and trigger 
the path in which they are interested. It is not a problem for crypto software 
since virtually all keys follow similar computational paths.

We use the amount of leaked information to represent the sensitivity level of 
each side-channel vulnerability. Although imperfect, \tool{} produces a reasonable 
measurement for each leak. For example, the simple modular exponentiation is 
notoriously famous for multiple side-channel attacks~\cite{kocher1996timing}. 
During the execution, a single leak point may execute multiple times
and each time leak a different bit. In this case, \tool{} reports that the 
vulnerability can leak the whole key. However, not every leak point inside a 
loop is severe. If a site in the loop leaks the same bit from the 
original key, and these leaks are not independent. \tool{} captures most 
fine-grained information by modeling each leak during the execution as a 
formula and the conjunction of the formulas to describe its total effect. 
Some leakage sites (e.g., square and multiply) 
can leak one particular bit of the original key, but some leakage sites leak one bit 
from several bytes in the original key. \tool{} can capture the dependency among the leaks and
reports more precise leakage information.

\tool{} reaches full precision if the number of estimated leaked bits 
equals to Definition~\ref{def}. 
\tool{} may lose precision from the 
memory model it uses in theory. However, we did not find false positives 
caused by the imprecise memory model during our evaluation. 
Sampling introduces imprecision but with a probabilistic guarantee. 
However, during the evaluation, we find that \tool{} cannot estimate 
the amount of leakage for some leakage sites in a reasonable time, 
which means the number of $K^o$ is very small. According to Definition~\ref{def}, 
it means the leakage is very severe. The sampling method in \S\ref{sec:scala} seems
simple and may miss some leakages (e.g., chosen ciphertext attacks) in theory. 
However, the evaluation result 
shows \tool{} can identify all leakages found by the previous work~\cite{203878,236338,Brotzman19Casym}.
